\documentclass[twoside]{article}
\usepackage{quiz}

\pagestyle{myheadings}

\lstset{
    language=Python,
    basicstyle=\ttfamily,
    showstringspaces=false
    keywordstyle=\color{black},
    commentstyle=\color{black},
    stringstyle=\color{black},
}

\def\semester{Fall 2016}

\newcommand{\solution}[1]{{\color{red}#1}}
% \newcommand\solution[1]{}

%%% Actual content begins here %%%
\title{\sc Discussion Quiz 8 \solution{Solutions}}

\begin{document}
\thispagestyle{empty}
\maketitle

\begin{enumerate}
%%% Question 1: Pin the Tail %%%
\q{3}{Pin the Tail}

Identify whether or not each of the following procedures uses a constant amount of space in a tail-recursive Scheme implementation (i.e. whether \textbf{every} recursive call is a tail call).

%%% Q1a %%%
\begin{lstlisting}
(define (copy lst result)
    (if (null? lst) result
        ((lambda (copy) copy) (copy (cdr lst)
                                    (append result (list (car lst)))))))
\end{lstlisting}

(Remember that {\tt append} takes zero or more lists and constructs a new list with all of the lists' elements.)

\solution{{\tt copy} is \emph{not} tail-recursive. After the recursive call returns, we still have to apply a {\tt lambda} procedure.}
\newline

%%% Q1b %%%
\begin{lstlisting}
(define (broken lst) (broken (broken lst)))
\end{lstlisting}

\solution{{\tt broken} is \emph{not} tail-recursive. One of the recursive calls is not a tail call.}
\newline

%%% Q1c %%%
\begin{lstlisting}
(define (is-ascending lst last-num)
    (if (null? lst) #t
        (and (is-ascending (cdr lst) (car lst)) (> (car lst) last-num))))
\end{lstlisting}

(Assume that this procedure is always called with a {\tt last-num} that is less than all of the elements in the list.)

\solution{{\tt is-ascending} is \emph{not} tail-recursive. The recursive call isn't even in a tail context!}
\newline

%%% Question 2: Hail Recursion %%%
\q{4}{Hail Recursion}

Write a \emph{tail-recursive} version of {\tt hailstone}. This procedure accepts a positive integer {\tt n} and returns a list that contains the hailstone sequence starting at {\tt n}. For instance, {\tt (hailstone 5)} would return {\tt (5 16 8 4 2 1)}.

\lstset{
    basicstyle=\ttfamily\color{red},
}

\begin{lstlisting}
(define (hailstone n)
  (define (hs-helper n lst)
    (cond ((= n 1) (append lst (list 1)))
          ((even? n) (hs-helper (/ n 2) (append lst (list n))))
          (else (hs-helper (+ 1 (* 3 n)) (append lst (list n))))))
  (hs-helper n nil))
\end{lstlisting}

%%% Question 3: Humans Need Not Apply %%%
\q{3}{Humans Need Not Apply}

What does {\tt eval} do, in the context of an interpreter? What does {\tt apply} do?

\solution{{\tt eval} parses expressions (all kinds of expressions; {\tt eval} doesn't discriminate!), \emph{evaluating} an expression's form to determine its meaning. On the other hand, {\tt apply} handles function calls (it \emph{applies} operators to arguments).

{\tt eval} and {\tt apply} are mutually recursive. Whenever {\tt eval} encounters a function call, it sends the expression to {\tt apply} to do the actual calling. In turn, {\tt apply} uses {\tt eval} to evaluate its arguments and to parse the body of user-defined functions.}

\end{enumerate}
\end{document}
